Iterative Monomorphisation

### 2024-03-22 iterative_monomorphisation.tex
small amount of editing

The iterative monomorphisation algorithm (Figure~\ref{iter_mono}) has two phases. The first phase applies a \emph{monomorphisation step} to each formula in \(\Phi\) until the user-set limit, \textcolor{ourblueviolet}{num\_loops}, is reached. This limit is the only bound necessary for the algorithm to terminate. We use the colour blue to identify bounds and for all code that is related to bounds. At the end of each of these iterations, the old and new type argument maps are updated with newly generated types. Once these iterations are completed, the first phase is completed and the substitutions used to create new type arguments are passed to the formula generation function for the second phase.

@@

Formula monomorphisation (Figure~\ref{mono_step}) computes new type arguments for a single formula. It forms the core of the monomorphisation process. A set of substitutions obtained from matching type argument tuples is iterated over. The separation of type arguments into old and new maps is put to use here. \emph{matches} (Figure~\ref{subst_gen}) is only called with at least one new type argument map. This avoids re-computing some of the matchings processed in previous iterations. Not all such redundant computations can be avoided because the same substitution can be obtained from different matchings. Each substitution is applied to all polymorphic type argument tuples such that at least one type variable in the tuple is instantiated by the substitution.

>>>>

The iterative monomorphisation algorithm (Figure~\ref{iter_mono}) has two phases. The first phase applies a \emph{monomorphisation step} to each formula in \(\Phi\) until the user-set limit, \textcolor{ourblueviolet}{num\_loops}, is reached. This limit is the only bound necessary for the algorithm to terminate. We use the colour blue to identify bounds and code related to bounds. At the end of each of these iterations, the old and new type argument maps are updated with newly generated types. Once these iterations are completed, the first phase is complete and the substitutions used to create new type arguments are passed to the formula generation function for the second phase.

@@

Formula monomorphisation (Figure~\ref{mono_step}) computes new type arguments for a single formula. It forms the core of the monomorphisation process. A set of substitutions obtained from matching type argument tuples is iterated over. The separation of type arguments into old and new maps is put to use here as \emph{matches} (Figure~\ref{subst_gen}) is not called on type argument maps which are both old. This avoids re-computing some of the matchings processed in previous iterations. Not all such redundant computations can be avoided because the same substitution can be obtained from different matchings. Each substitution is applied to all polymorphic type argument tuples such that at least one type variable in the tuple is instantiated by the substitution.
